\vskip-0.6in LOBBYING AND LEGISLATIVE UNCERTAINTY

### 2016-02-15 draft.tex
rough in results section

\subsection{Vote Buyer B}
Groseclose and Snyder (1996) assume that the objective of each vote buyer is to ``minimize total bribes paid while passing his preferred policy.'' This has to be adapted out our environment with uncertainty about legislators' ideal points. The appropriate analog is that vote buyers maximize the expected value of winning the vote net of bribes that he/she must pay. Note that in order to maximize the probability of winning a majority in a three-seat legislature, one must maximize the probability of at least two legislators voting with you. The case of Vote Buyer $B$, this is the probability that at least two legislators vote in favor of the status quo: $\Pr(S \geq 2)$ where $S = X\left(-\frac{1}{2}\right) + X\left(0\right) + X\left(\frac{1}{2}\right)$.

@@

\subsection{Vote Buyer B}

@@

\begin{proposition}
  When Vote Buyer $B$ pays bribes to exactly two legislators, the bribes are such that the two bribed legislators' ideal points net of the bribes are equalized. Which two voters are bribed depends on the bias parameter $\al$.
	\label{prop:2NNB}
\end{proposition}

@@

\begin{itemize}

			\item They can easily both have positive probability of winning. But what do we need for this to be an equilibrium in this three stage game?
			\item Uncertainty buys us a lot: no longer this knife edge condition of $A$ pushing to the point that $B$ buys no votes
			\item Note the non-negativity constraint means you can't extract money from a legislator who is past the FOC point in order to reallocate to another legislator
			\item Some legislators who are past FOC point will not be lobbied

@@

\vskip.1in
The only intuition I see for why the next legislator is added in is that it's when the additional expense is justified by the increase in winning probability, conditional on the rule that 2+ legislators have to have the same gross ideal point
\begin{itemize}
	\item I think it's actually that the next legislator is added when the non-negativity constraint stops binding; that is, when $W_B$ becomes high enough that the additional probability of winning is worth the additional cost
	\item What's the intuition for why they should be equal? As far as I can tell, it's that the PDF is unimodal. If the ideal points are very close, you don't want to continue moving one and leave the other behind because the marginal increase will be greater for whichever is to the left.
	\item \textbf{Next question: How general is this result? That is, how much asymmetry can I have in the logistic distribution, $\beta$s, and for how broad a class of distributions would it hold? My conjecture is that it leans on having an interior single mode}
\end{itemize}

\subsection{Varying Uncertainty across Legislators}
\label{sec:resunc}
Numerical example. Take $\al=0$ and ignore A. Take $s_{.5}$ from 1 to 1.5. $B$ stops bribing legislator $0.5$ (least friendly) altogether. Does better in welfare terms because the probability this guy votes in his favor shifts up
		\begin{itemize}
			\item For $s_{.5} = 1.1$, no bribe for $0.5$ guy until $W_B$ gets significantly higher, and then his net position is lower than $X=Y$
			\item At $s_{.5} = .75$: ONLY Z for $W_B \in \left[6,8\right]$ (8 is usually where it's $X$ alone). Then $Z$ and $Y$ together but $Z$ further on net than $Y$. Eventually all three, with $X=Y$, $Z$ further
		\end{itemize}
Numerical example. Take $\al=0$ and ignore A. Take $s_{-.5}$ from 1 to 2. $B$ stops bribing legislator $-0.5$ (most friendly) altogether.
		\begin{itemize}
			\item This is true even with $s_{-.5}$ as low as 1.2 (taking $s_{.5} = s_{0} = 1$)
			\item For $1 < s_{-.5} < 1.2$, no bribe for $-0.5$ guy until $W_B$ gets significantly higher, and then his net position is lower than $X=Z$
			\item Reverse if $s_{-.5} < 1$: move $-0.5$ guy further left than $X=Z$ (but not further than $X$ when just these two); in some cases leave $0.5$ guy at zero
		\end{itemize}

\subsection{Two Vote Buyers}

@@

\begin{figure}
\centering
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=2.9in]{graph2.jpg}
  \caption{\smallLobbying Effort and Support for KORUS
	\label{fig:br}}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=2.9in]{graph1.jpg}
  \caption{\smallNet Campaign Contributions, KORUS
	\label{fig:g1}}
\end{minipage}
\end{figure}

>>>>

\subsection{Vote Buyer B}
Groseclose and Snyder (1996) assume that the objective of each vote buyer is to ``minimize total bribes paid while passing his preferred policy.'' This has to be adapted out our environment with uncertainty about legislators' ideal points, as with any probability distribution with infinite support both players will necessarily have a positive probability of winning in equilibrium regardless of their strategies. The appropriate analog is that vote buyers maximize the expected value of winning the vote net of bribes that he/she must pay. Note that in order to maximize the probability of winning a majority in a three-seat legislature, one must maximize the probability of at least two legislators voting with you. The case of Vote Buyer $B$, this is the probability that at least two legislators vote in favor of the status quo: $\Pr(S \geq 2)$ where $S = X\left(-\frac{1}{2}\right) + X\left(0\right) + X\left(\frac{1}{2}\right)$.

@@

\subsection{Vote Buyer B}
\label{sec:resB}

@@

\begin{proposition}
  When Vote Buyer $B$ pays bribes to exactly two legislators, the bribes are such that the two bribed legislators' ideal points gross of bribes are equalized. Which two voters are bribed depends on the bias parameter $\al$.
	\label{prop:2NNB}
\end{proposition}

@@

\begin{proposition}
  When Vote Buyer $B$ pays bribes to exactly one legislator, ... can be any one, not necessarily ideologically closest.
	\label{prop:1NNB}
\end{proposition}
In contrast to models with no uncertainty about legislators' ideological positions, here we have an anti-result that the vote buyers do not necessarily bribe those who are ideologically most aligned with themselves. The non-negativity constraint often rules out bribing the most friendly legislator(s) because she/they don't contribute very much to the overall probability of winning the issue.

Figure~\ref{fig:br} shows an example of a vote in which the most money went to the ideologically moderate--not the most extreme in a `leveling' strategy.

\begin{proposition}
  When Vote Buyer $B$ pays bribes to all three legislators, the bribes are such that the legislators' ideal points gross of bribes are equalized.
	\label{prop:3NNB}
\end{proposition}

\begin{itemize}
			\item Note the non-negativity constraint means you can't extract money from a legislator who is past the FOC point in order to reallocate to another legislator
			\item Some legislators who are past FOC point will not be lobbied

@@

\vskip.1in
The only intuition I see for why the next legislator is added in is that it's when the additional expense is justified by the increase in winning probability, conditional on the rule that 2+ legislators have to have the same gross ideal point
\begin{itemize}
	\item I think it's actually that the next legislator is added when the non-negativity constraint stops binding; that is, when $W_B$ becomes high enough that the additional probability of winning is worth the additional cost
	\item What's the intuition for why they should be equal? As far as I can tell, it's that the PDF is unimodal. If the ideal points are very close, you don't want to continue moving one and leave the other behind because the marginal increase will be greater for whichever is to the left.
\end{itemize}

\subsection{Varying Uncertainty across Legislators}
\label{sec:resunc}

The results of Section~\ref{sec:resB} in which bribed legislators have their ideal points `leveled' so that their positions gross of bribes are equalized evidently hinge on the symmetry in uncertainty assumed there.

\begin{proposition}
  test
\end{proposition}
Very low, very high uncertainty gets lowest payments, middle uncertainty gets most (Figure \ref{fig:g1}.

\vskip.2in
Numerical example. Take $\al=0$ and ignore A. Take $s_{.5}$ from 1 to 1.5. $B$ stops bribing legislator $0.5$ (least friendly) altogether. Does better in welfare terms because the probability this guy votes in his favor shifts up
		\begin{itemize}
			\item For $s_{.5} = 1.1$, no bribe for $0.5$ guy until $W_B$ gets significantly higher, and then his net position is lower than $X=Y$
			\item At $s_{.5} = .75$: ONLY Z for $W_B \in \left[6,8\right]$ (8 is usually where it's $X$ alone). Then $Z$ and $Y$ together but $Z$ further on net than $Y$. Eventually all three, with $X=Y$, $Z$ further
		\end{itemize}
Numerical example. Take $\al=0$ and ignore A. Take $s_{-.5}$ from 1 to 2. $B$ stops bribing legislator $-0.5$ (most friendly) altogether.
		\begin{itemize}
			\item This is true even with $s_{-.5}$ as low as 1.2 (taking $s_{.5} = s_{0} = 1$)
			\item For $1 < s_{-.5} < 1.2$, no bribe for $-0.5$ guy until $W_B$ gets significantly higher, and then his net position is lower than $X=Z$
			\item Reverse if $s_{-.5} < 1$: move $-0.5$ guy further left than $X=Z$ (but not further than $X$ when just these two); in some cases leave $0.5$ guy at zero
		\end{itemize}

\subsection{Two Vote Buyers}		
Uncertainty buys us a lot: no longer this knife edge condition of $A$ pushing to the point that $B$ buys no votes

\begin{proposition}
  It is possible for both vote buyers to bribe legislators on the same vote.
\end{proposition}

\begin{proposition}
  It is possible that neither vote buyer bribes any legislator on a given vote. This occurs when both vote buyers' willingness-to-pay parameters are small.
\end{proposition}

@@

\begin{figure}
\centering
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=2.9in]{graph2.jpg}
  \caption{\small Lobbying Effort and Support for KORUS
	\label{fig:br}}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[width=2.9in]{graph1.jpg}
  \caption{\small Net Campaign Contributions, KORUS
	\label{fig:g1}}
\end{minipage}
\end{figure}
